### 2017-02-01 local-capability-machine.tex
global cap vr
Change malloc spec slightly so that c_malloc is hopefully in the value relation.  Specify the latter fact as an (unproven so far) lemma.

              \begin{specification}[Malloc v.2]
                $c_\malloc$ satisfies the specification for malloc iff
                \[  
                  \begin{aligned}
                    &\exists \iota_{\malloc,0} \ldotp \\
                    &\quad (\forall \iota' \futurestr \iota_{\malloc,0} \ldotp \forall W,i \ldotp W(i)=\iota' \Rightarrow \iota'.H (\iota'.s) (W) = \iota'.H (\iota'.s) ([i \mapsto W(i)]) ) \; \land \\
                    &\quad \iota_{\malloc,0}.v = \perma \; \land \\
                    &\quad (\forall \Phi \in \ExecConfs \ldotp \forall \ms_{\var{footprint}}, \hsframe \in \HeapSegments \ldotp \\
                    &\qquad \forall i, n, \size \in \nats \ldotp \forall b,e,a \in \Addrs\ldotp\forall p \in \Perms \ldotp \\
                    &\qquad \quad \forall \iota_\malloc \futurestr \iota_{\malloc,0} \land \\
                    &\qquad \quad \memheap = \ms_{\var{footprint}} \uplus \hsframe \land\\
                    &\qquad \quad \heapSat[\ms_{\var{footprint}}]{n}{[i \mapsto \iota_\malloc]} \land \\
                    &\qquad \quad \memreg(r_1) = \size \land \\
                    &\qquad \quad \size \geq 0 \land \\
                    &\qquad \quad \memreg(r_0) = (p,b,e,a) \land \\
                    &\qquad \quad \memreg(\pcreg) = c_\malloc \\ %and this needs to change with ABI.
                    &\qquad \quad \Rightarrow \\
                    &\qquad \qquad\exists \Phi' \in \ExecConfs \ldotp \exists \ms_{\var{footprint}}', \ms_{\var{alloc}} \in \HeapSegments\ldotp\\
                    &\qquad \qquad \quad \exists j \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \exists \iota_\malloc' \in \Regions \ldotp \\
                    &\qquad \qquad \qquad \Phi \step[j] \Phi' \land \\
                    &\qquad \qquad \qquad \memheap[\Phi']=\ms_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land\\
                    &\qquad \qquad \qquad \iota_{\malloc}' \futurewk \iota_\malloc \land \\
                    &\qquad \qquad \qquad \heapSat[\ms_{\var{footprint}}']{n-j}{[i \mapsto \iota_\malloc']} \land \\
                    &\qquad \qquad \qquad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land \\
                    &\qquad \qquad \qquad \memreg[\Phi'] = \memreg[\Phi]\update{\pcreg}{\updatePcPerm{(p,b,e,a)}}\update{r_1}{((\rwx,\glob),b',e',b')} \land \\
                    &\qquad \qquad \qquad \size - 1 = e'-b' )
                  \end{aligned}
                \]
              \end{specification}
              In the specification above $\iota_\malloc'$ is a future region of the initial region that governs malloc.
              \lau{What about $c_\malloc$ and the value relation? Do we add this to the specification or try to prove it based on the specification?}

@@

>>>>

              \begin{specification}[Malloc v.2]
                $c_\malloc$ satisfies the specification for malloc iff
                \[  
                  \begin{aligned}
                    &c_\malloc = ((\entry,\_),\_,\_,\_) \land\\
                    &\exists \iota_{\malloc,0} \ldotp \\
                    &\quad (\forall \iota' \futurestr \iota_{\malloc,0} \ldotp \forall W,i \ldotp W(i)=\iota' \Rightarrow \iota'.H (\iota'.s) (W) = \iota'.H (\iota'.s) ([i \mapsto W(i)]) ) \; \land \\
                    &\quad \iota_{\malloc,0}.v = \perma \; \land \\
                    &\quad (\forall \Phi \in \ExecConfs \ldotp \forall \ms_{\var{footprint}}, \hsframe \in \HeapSegments \ldotp \\
                    &\qquad \forall i, n, \size \in \nats \ldotp \forall b,e,a \in \Addrs\ldotp\forall p \in \Perms \ldotp \\
                    &\qquad \quad \forall \iota_\malloc \futurestr \iota_{\malloc,0} \land \\
                    &\qquad \quad \memheap = \ms_{\var{footprint}} \uplus \hsframe \land\\
                    &\qquad \quad \heapSat[\ms_{\var{footprint}}]{n}{[i \mapsto \iota_\malloc]} \land \\
                    &\qquad \quad \memreg(r_1) = \size \land \\
                    &\qquad \quad \size \geq 0 \land \\
                    &\qquad \quad \memreg(r_0) = (p,b,e,a) \land \\
                    &\qquad \quad \memreg(\pcreg) = \updatePcPerm{c_\malloc} \\ %and this needs to change with ABI.
                    &\qquad \quad \Rightarrow \\
                    &\qquad \qquad\exists \Phi' \in \ExecConfs \ldotp \exists \ms_{\var{footprint}}', \ms_{\var{alloc}} \in \HeapSegments\ldotp\\
                    &\qquad \qquad \quad \exists j \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \exists \iota_\malloc' \in \Regions \ldotp \\
                    &\qquad \qquad \qquad \Phi \step[j] \Phi' \land \\
                    &\qquad \qquad \qquad \memheap[\Phi']=\ms_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land\\
                    &\qquad \qquad \qquad \iota_{\malloc}' \futurewk \iota_\malloc \land \\
                    &\qquad \qquad \qquad \heapSat[\ms_{\var{footprint}}']{n-j}{[i \mapsto \iota_\malloc']} \land \\
                    &\qquad \qquad \qquad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land \\
                    &\qquad \qquad \qquad \memreg[\Phi'] = \memreg[\Phi]\update{\pcreg}{\updatePcPerm{(p,b,e,a)}}\update{r_1}{((\rwx,\glob),b',e',b')} \land \\
                    &\qquad \qquad \qquad \size - 1 = e'-b' )
                  \end{aligned}
                \]
              \end{specification}
              In the specification above $\iota_\malloc'$ is a future region of the initial region that governs malloc.
              \lau{What about $c_\malloc$ and the value relation? Do we add this to the specification or try to prove it based on the specification?}

@@

\subsubsection{Malloc safe to pass to adversary}
\label{sec:malloc-valrel}

\begin{lemma}[Malloc is safe to pass to adversary]
  If $W(r) = \iota$ with $\iota \futw \iota_{\malloc,0}$, then
  $\npair{c_\malloc} \in \stdvr(W)$ for all $n$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}
